Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2012-11-30 large_number_squeezing_with_atoms.tex
Inserted pi pulse figure into paper

\begin{figure}
    \centering
    \includegraphics[width=8cm]{figures/piPulseFig.eps}
    \caption{This is a picture of a $\pi$-pulse working.}
    \label{piPulseFig}
\end{figure}

\section{Squeezing in 2D and 3D}
The simulations in the previous two sections were one dimensional, and show how having spatially constant density and using a $\pi$-pulse will improve the resultant squeezing.  While these conclusions remain valid for simulations in two or three dimensions, adding each additional dimension results in a degradation of the squeezing.  This is true even when the potential (and the resulting atomic density) is constant across the bulk of the trap.  Furthermore, the expected squeezing goes down as the volume of the trap increases.  This can be seen in Fig.~\ref{1D2D3DworsererFig}, where we show the squeezing generated \textbf{by 1D, 2D and 3D BECs in a box with some parameters}.

\begin{figure}
    \centering
    \includegraphics[width=8cm]{figures/1D2D3DBox.eps}
    \caption{Even BECs in a box get worse with both dimension and volume.}
    \label{1D2D3DworsererFig}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=8cm]{figures/pi_pulse.eps}
    \caption{Effect of a $\pi$-pulse halfway through the hold time. Common parameters: $n_a = n_b =2 \times 10^5$, $\chi_{aa}=0.03\hbar$, $\chi_{ab}=\chi_{bb}=0$. Solid red line: Analytic two-mode solution, $\tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=3.0$ (10.9dB squeezing); Solid blue line: no $\pi$-pulse, $\tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=3.0$ (4.9dB squeezing);  Dashed blue line: with $\pi$-pulse, $\tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=3.05$ (5.8dB squeezing); Dash-dotted blue line: with $\pi$-pulse, $\tau_{\mathrm{hold}}=5\times 10^{-4}$s, $\phi=3.87$ (7.2dB squeezing).}
    \label{piPulseFig}
\end{figure}

\section{Squeezing in 2D and 3D}
The simulations in the previous two sections were one dimensional, and show how having spatially constant density and using a $\pi$-pulse will improve the resultant squeezing.  While these conclusions remain valid for simulations in two or three dimensions, adding each additional dimension results in a degradation of the squeezing.  This is true even when the potential (and the resulting atomic density) is constant across the bulk of the trap.  Furthermore, the expected squeezing goes down as the volume of the trap increases.  This can be seen in Fig.~\ref{figDimensionalSqueezingEffects}, where we show the squeezing generated \textbf{by 1D, 2D and 3D BECs in a box with some parameters}.
